Resource Allocation in an Open RAN System using Network Slicing\vspace{-.1cm}

### 2021-08-21 Latex/journal_v1/V5/pr.tex
add feasible part

\author{\IEEEauthorblockN{1\textsuperscript{st} Mojdeh Karbalaee Motalleb}
\IEEEauthorblockA{\textit{Electrical and Computer Engineering} \\
\textit{Tehran University}\\
Tehran, Iran \\
mojdeh.karbalaee@ut.ac.ir}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Vahid Shah-Mansouri}
\IEEEauthorblockA{\textit{Electrical and Computer Engineering} \\
\textit{Tehran University}\\
Tehran, Iran \\
vmansouri@ut.ac.ir}
%\and
%\IEEEauthorblockN{3\textsuperscript{rd} Salar Nouri Naghadeh}
%\IEEEauthorblockA{\textit{Electrical and Computer Engineering} \\
%\textit{Tehran University}\\
%Tehran, Iran \\
%salar.nouri@ut.ac.ir}
%}
%  \author{
%    \IEEEauthorblockN{Mojdeh Karbalaee Motalleb, Vahid Shah-mansouri}
%    \IEEEauthorblockA{School of ECE, College of Engineering, University of Tehran, Iran \\
%    Email: \{mojdeh.karbalaee, vmansouri\}@ut.ac.ir,
%    \vspace{-.2cm}
%  }
 }

@@

\section{Numerical Results}\label{NE}
In this section, numerical results for the main problem are depicted to evaluate the performance of the algorithms using the Monte-Carlo method. We consider three network slices for eMBB, URLLC, and mMTC services.

@@

Here, The channel vector from the O-RU $r$ to the UE $i$ in service $s$ is set as $\bold{h}_{r,u(s,i)}^{k}=d_{r,u(s,i)}^{-\mathcal{L}} \Omega_{r,u(s,i)}^{k} $.  Where, $d_{r,u(s,i)}^{-\mathcal{L}} $ is the distance between the O-RU $r$ and the UE $i$ in service $s$ and $\mathcal{L} = 3.8$ is the path-loss exponent \cite{gholipoor2020cloud}.

@@

Two different methods are used to compare with the performance of the proposed method (IABV).
 The first one is a baseline scheme, which used random PRB allocation. The association of O-RU is only based on the distance. Also, the number of activated VNF for each slice is fixed.

Finding a feasible initial value is almost tricky. To overcome this challenge, we compare it with the baseline scheme method using the CVX of Matlab which used successive convex approximation (SCA) method. If the baseline scheme converged and has a feasible solution, so our algorithm (IABV) can be converged too.

@@

In Fig. \ref{fig:1} the aggregate throughput is demonstrated versus the different number of UEs in each service for these three methods. Suppose we have one service instance for each type of service, so we have three various services in this figure. Also We have between 6 and 48 UEs in the system.
Here, we did not consider the priority. The figure presented that the proposed method (IABV) is $18.6\%$ higher than the baseline scheme.
As the number of UEs increases in each service, the aggregated throughput initially increases. Still, due to the interference and the power constraint, it will be saturated from 12 UEs in each service.
\begin{figure}
  \centering 
    \includegraphics[scale = 0.47]{Arate_ue1.eps}
    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
    %\includegraphics[width=\textwidth]{finalDraw.pdf}
  \caption{Aggregate Throughput vs. Number of UE in each Service In the Presence of Three Services}
  \label{fig:1}
\end{figure}
%Assume we have two type of services (URLLC and mMTC). In figure \ref{fig:2} and \ref{fig:3}, the aggregate throughput (by considering the priority factor 
%($\sum_s \sum_i \delta_s \bar{R}_{{u(s,i)}}$)) is depicted for two services URLLC and mMTC. Here we consider 4 UEs in each service. The other parameter is shown in table \ref{table:1a}.
%The figure \ref{fig:2}, presented that by increasing the priority factor for URLLC, more resources is allocated to this service and the aggregate throughput of this service is increased and vice verse.
%\begin{figure}
%  \centering 
%    \includegraphics[scale = 0.4]{mmtcurllc.eps}
%    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
%    %\includegraphics[width=\textwidth]{finalDraw.pdf}
%  \caption{Aggregate Throughput for mMTC and URLLC vs. Priority of URLLC }
%  \label{fig:2}
%\end{figure}
%In figure \ref{fig:3}, the total sum rate of URLLC and mMTC is shown vs. priority of URLLC. It is shown that the proposed method is much better than the baseline scheme. 
%\begin{figure}
%  \centering 
%    \includegraphics[scale = 0.4]{sumRatePri.eps}
%    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
%    %\includegraphics[width=\textwidth]{finalDraw.pdf}
%  \caption{Aggregate Throughput of all services vs. Priority of URLLC}
%  \label{fig:3}
%\end{figure}

@@

\begin{figure}
  \centering 
    \includegraphics[scale = 0.4]{interF.eps}
    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
    %\includegraphics[width=\textwidth]{finalDraw.pdf}
  \caption{Aggregate Throughput vs. Maximum Interference }
  \label{fig:13}
\end{figure}
\section{Conclusion}\label{conc}
This paper proposed the downlink of the O-RAN system using network slicing for different types of 5G services i.e eMBB, mMTC, and, URLLC.
The isolation of various types of services i.e eMBB, mMTC, and, URLLC in the O-DU, the O-CU, and the user plane function (UPF) is accomplished.
Also, the paper aims to obtain the number of activated VNFs in each service, RU association, power, and PRB allocation to maximize the aggregate throughput. The limited fronthaul capacity and the mean end-to-end delay for each service are considered. 
The problem is mixed-integer non-linear programming that is solved by the two-step iterative algorithm.
In the first step, we reformulated the problem to achieve the number of activated VNFs as a function of data rate. Then we obtain PRB association and power allocation using the Lagrangian method.
Then in the second step, the O-RU association is acquired.
The performance of our proposed method (IABV) is compared with the baseline scheme and FBDR in \cite{lee2018dynamic}. 
Also, we assume distinct scenarios for each service i.e eMBB, mMTC, and, URLLC based on their requirement QoS.
Simulation results depict that the proposed method (IABV) achieved $18.6\%$ higher data rate than the baseline scheme.
Moreover, simulation results illustrate more minor delays for the proposed method (IABV) than FBDR and the baseline scheme.

>>>>

\author{\IEEEauthorblockN{1\textsuperscript{st} Mojdeh Karbalaee Motalleb}
\IEEEauthorblockA{\textit{Electrical and Computer Engineering} \\
\textit{Tehran University}\\
Tehran, Iran \\
mojdeh.karbalaee@ut.ac.ir}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Vahid Shah-Mansouri}
\IEEEauthorblockA{\textit{Electrical and Computer Engineering} \\
\textit{Tehran University}\\
Tehran, Iran \\
vmansouri@ut.ac.ir}
\and
\IEEEauthorblockN{3\textsuperscript{rd} Saeedeh Parsaeefard}
\IEEEauthorblockA{\textit{Electrical and Computer Engineering} \\
\textit{University of Toronoto}\\
Toronoto, Canada \\
aeede.parsaeefard@gmail.com}
}
%  \author{
%    \IEEEauthorblockN{Mojdeh Karbalaee Motalleb, Vahid Shah-mansouri}
%    \IEEEauthorblockA{School of ECE, College of Engineering, University of Tehran, Iran \\
%    Email: \{mojdeh.karbalaee, vmansouri\}@ut.ac.ir,
%    \vspace{-.2cm}
%  }

@@

\section{Numerical Results and The Feasible Region}\label{NE}
In this section, firstly we describe the initial points and the comparison algorithms.
Then we talk about the feasible region in our system. 
Afterward, we illustrated the numerical results.
\subsection{The initial Points and The Comparison Algorithms}
In this part, numerical results for the main problem are depicted to evaluate the performance of the algorithms using the Monte-Carlo method. We consider three network slices for eMBB, URLLC, and mMTC services.

@@

Here, the channel vector from the O-RU $r$ to the UE $i$ in service $s$ is set as $\bold{h}_{r,u(s,i)}^{k}=d_{r,u(s,i)}^{-\mathcal{L}} \Omega_{r,u(s,i)}^{k} $.  Where, $d_{r,u(s,i)}^{-\mathcal{L}} $ is the distance between the O-RU $r$ and the UE $i$ in service $s$ and $\mathcal{L} = 3.8$ is the path-loss exponent \cite{gholipoor2020cloud}.

@@

Finding a feasible initial value is almost tricky. To overcome this challenge, we use a fast method that we talk about it in the \ref{fr}. If the fast method converged and has a feasible solution, so our algorithm (IABV) can be converged too.

Two different methods are used to compare with the performance of the proposed method (IABV) and show the optimality of our approach.
 The first one is a baseline scheme, which used random PRB allocation. The association of O-RU is only based on distance. Also, the number of activated VNF for each slice is fixed. The optimal power
 is obtained using the CVX of Matlab, which used the successive convex approximation (SCA) method.

@@

\subsection{Feasible Region}\label{fr}
Applying the correct initial point to make the system feasible is a significant step in our work.
During the simulation, it can be noted that sometimes the algorithm does not converge in a number of these simulations for a certain number of UEs.
For a fixed number of UEs, by comparing convergent and non-convergent simulations, we experimentally found that in cases where convergence does not occur, UEs are at the edge of the boundaries or far away from the O-RU and have a weak channel gain. One solution is to eliminate UEs who undermine system convergence.
Another solution is to remove the simulations in the mont-Carlo that do not converge.
To remove non-converging simulations, we need to use a fast algorithm (FA) to check the convergence before
the proposed algorithm (IABV). 
If the conditions \eqref{RConstr}, \eqref{pr11}, \eqref{c12-1} and \eqref{c12} are met in the fast algorithm (FA), the given algorithm will converge.
The FA algorithm is depicted as algorithm \ref{alg3}.
\caption{Fast Algorithm to Check the Convergence}\label{alg3}
\State Assume the number of UEs is $\mathfrak{N} = \sum_{s=1}^{S}\sum_{i=1}^{U_S}1$
\State Set $p_{r,u(s,i)}^{k} = \min\{P_s^{max}, P_r^{max}/\mathfrak{N}\} \quad \forall r,s,i,k$
\State Set 
\subsection{Numerical Results}
In Fig. \ref{fig:1} the aggregate throughput is demonstrated versus the different number of UEs in each service for these three methods. Suppose we have one service instance for each type of service, so we have three various services in this figure. Also We have between 6 and 48 UEs in the system.
Here, we did not consider the priority. The figure presented that the proposed method (IABV) is $18.6\%$ higher than the baseline scheme.
As the number of UEs increases in each service, the aggregated throughput initially increases. Still, due to the interference and the power constraint, it will be saturated from 12 UEs in each service.
    \includegraphics[scale = 0.47]{Arate_ue1.eps}
  \caption{Aggregate Throughput vs. Number of UE in each Service In the Presence of Three Services}
  \label{fig:1}
%Assume we have two type of services (URLLC and mMTC). In figure \ref{fig:2} and \ref{fig:3}, the aggregate throughput (by considering the priority factor 
%($\sum_s \sum_i \delta_s \bar{R}_{{u(s,i)}}$)) is depicted for two services URLLC and mMTC. Here we consider 4 UEs in each service. The other parameter is shown in table \ref{table:1a}.
%The figure \ref{fig:2}, presented that by increasing the priority factor for URLLC, more resources is allocated to this service and the aggregate throughput of this service is increased and vice verse.
%\begin{figure}
%  \centering 
%    \includegraphics[scale = 0.4]{mmtcurllc.eps}
%    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
%    %\includegraphics[width=\textwidth]{finalDraw.pdf}
%  \caption{Aggregate Throughput for mMTC and URLLC vs. Priority of URLLC }
%  \label{fig:2}
%\end{figure}
%In figure \ref{fig:3}, the total sum rate of URLLC and mMTC is shown vs. priority of URLLC. It is shown that the proposed method is much better than the baseline scheme. 
%\begin{figure}
%  \centering 
%    \includegraphics[scale = 0.4]{sumRatePri.eps}
%    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
%    %\includegraphics[width=\textwidth]{finalDraw.pdf}
%  \caption{Aggregate Throughput of all services vs. Priority of URLLC}
%  \label{fig:3}
%\end{figure}

@@

\begin{figure}
  \centering 
    \includegraphics[scale = 0.4]{interF.eps}
    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
    %\includegraphics[width=\textwidth]{finalDraw.pdf}
  \caption{Aggregate Throughput vs. Maximum Interference }
  \label{fig:13}
\end{figure}

\section{Conclusion}\label{conc}
This paper proposed the downlink of the O-RAN system using network slicing for different types of 5G services i.e eMBB, mMTC, and, URLLC.
The isolation of various types of services i.e eMBB, mMTC, and, URLLC in the O-DU, the O-CU, and the user plane function (UPF) is accomplished.
Also, the paper aims to obtain the number of activated VNFs in each service, RU association, power, and PRB allocation to maximize the aggregate throughput. The limited fronthaul capacity and the mean end-to-end delay for each service are considered. 
The problem is mixed-integer non-linear programming that is solved by the two-step iterative algorithm.
In the first step, we reformulated the problem to achieve the number of activated VNFs as a function of data rate. Then we obtain PRB association and power allocation using the Lagrangian method.
Then in the second step, the O-RU association is acquired.
The performance of our proposed method (IABV) is compared with the baseline scheme and FBDR in \cite{lee2018dynamic}. 
Also, we assume distinct scenarios for each service i.e eMBB, mMTC, and, URLLC based on their requirement QoS.
Simulation results depict that the proposed method (IABV) achieved $18.6\%$ higher data rate than the baseline scheme.
Moreover, simulation results illustrate more minor delays for the proposed method (IABV) than FBDR and the baseline scheme.
